Behavior Driven Development in Haskell

### 2012-05-28 paper.tex
writing related work.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Open problems and related work}
\begin{itemize}
    \item literate programming.
    \item hunit.
    \item test-framework.
    \item smallCheck.
    \item And others?
    \item The {\tt testpack} package provides a function that is
        similar in purpose to {\tt shouldThrow}.

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Open problems and related work}

SmallCheck~\cite{smallcheck} is a tool for
automatic exhaustive testing at a certain level.
Both Doctest and Hspec do not have support for SmallCheck
at this moment.

The {\tt test-framework} family is a TDD tool, 
which currently integrates HUnit, QuickCheck, SmallCheck, and Doctest.
Automatic test discovery based on prefixes of function name
and is implemented using Template Haskell.

\begin{itemize}
    \item The {\tt testpack} package provides a function that is
        similar in purpose to {\tt shouldThrow}.

@@

        @sol: Let's add this.
